Implementation and comparison of register allocation to translate \lstinline!LLVM--! to x86

### 2023-11-27 article.tex
Fix references

The process of assigning each variable to a GPR is referred to as \textit{register allocation}, and can be approached in several different ways. This paper will seek to implement graph coloring and linear scan and evaluate them in terms of runtime performance after compilation. %% TODO: compare with time-complexity/compile-time duration?
The primary sources will be \textit{Modern Compiler Implementation in ML} \parencite{AppelAndrewW} and \textit{Compilers: Principles, techniques, and tools} by \parencite{alma99122774374105763}, in addition to scientific publications concerning the linear scan approach.

@@

The two primary sources are the \textit{Modern Compiler Implementation in ML} \cite{AppelAndrewW} and Dragonbook \cite{alma99122774374105763}, in addition to scientific publications concerning the linear scan approach.

@@

The algorithm described in \textit{Modern Compiler Implementation in ML} \cite{AppelAndrewW} and \cite{alma99122774374105763} is based on the following equations for the live-in and live-out variables respectively:
\begin{align}
  in\left[n\right] &= use\left[n\right] \cup (out\left[n\right] - \mathit{def}\left[n\right])\\
  out\left[n\right] &= \bigcup_{s\in \mathit{succ}\left[n\right]} in\left[s\right]
\end{align}
where \(use\left[n\right]\) is the set of all dependent variables, \(def\left[n\right]\) is the set of all variables defines and \(succ\left[n\right]\) is the set of all immediate successor nodes of \(n\).

The structure of the CFG is inherently vague as both   \cite{AppelAndrewW} and \textit{Compilers : Principles, Techniques, and Tools} \cite{alma99122774374105763}, while based on the same underlying % TODO: fix references
conceptions of dataflow, have different approaches to nodes of a CFG, with the former taking each individual instruction into consideration and the latter each basic block. Either of these approaches are sound

@@

In contrast, the x86 \textit{instruction set architecture} (ISA) is targeting a  \textit{complex instruction set computer} (CISC) family of processors, the instructions of which perform a much broader set of operations \cite[p.~190]{AppelAndrewW}. This is is in part due to pipelining, i.e. an abstraction over the concrete implementation of the actual processor, which in turn is made for the sake of performance.

>>>>

The process of assigning each variable to a GPR is referred to as \textit{register allocation}, and can be approached in several different ways. This paper will seek to implement graph coloring and linear scan and evaluate them in terms of runtime performance after compilation. %% TODO: compare with time-complexity/compile-time duration?
The primary sources will be \textit{Modern Compiler Implementation in ML} \parencite{tiger} and \textit{Compilers: Principles, techniques, and tools} \parencite{dragon}, in addition to publications concerning the linear scan approach.

@@

The two primary sources are the \textit{Modern Compiler Implementation in ML} \cite{tiger} and Dragonbook \cite{dragon}, in addition to scientific publications concerning the linear scan approach.

@@

The algorithm described in \textit{Modern Compiler Implementation in ML} \cite{tiger} and \cite{dragon} is based on the following equations for the live-in and live-out variables respectively:
\begin{align}
  in\left[n\right] &= use\left[n\right] \cup (out\left[n\right] - \mathit{def}\left[n\right])\\
  out\left[n\right] &= \bigcup_{s\in \mathit{succ}\left[n\right]} in\left[s\right]
\end{align}
where \(use\left[n\right]\) is the set of all dependent variables, \(def\left[n\right]\) is the set of all variables defines and \(succ\left[n\right]\) is the set of all immediate successor nodes of \(n\).

The structure of the CFG is inherently vague as both   \cite{tiger} and \textit{Compilers : Principles, Techniques, and Tools} \cite{dragon}, while based on the same underlying % TODO: fix references
conceptions of dataflow, have different approaches to nodes of a CFG, with the former taking each individual instruction into consideration and the latter each basic block. Either of these approaches are sound

@@

In contrast, the x86 \textit{instruction set architecture} (ISA) is targeting a  \textit{complex instruction set computer} (CISC) family of processors, the instructions of which perform a much broader set of operations \cite[p.~190]{tiger}. This is is in part due to pipelining, i.e. an abstraction over the concrete implementation of the actual processor, which in turn is made for the sake of performance.
